\documentclass{sig-alternate}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{color}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{flushend}
\usepackage{cite,float}
\usepackage[normalem]{ulem}
\usepackage{verbatim}
%\usepackage{subfig}
\usepackage{subfigure}

%\newtheorem{theorem}{Theorem}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{axiom}{Axiom}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}{Definition}[section]
%
%\newcounter{defCount}
%\newenvironment{definition}[1][Definition]{
%    \refstepcounter{defCount}
%    \begin{trivlist}
%    \item[\hskip \labelsep
%        {\bfseries Definition \arabic{defCount} #1}]}
%    {\end{trivlist}}

\newcounter{coroCount}
\newenvironment{corollary}[1][]{
    \refstepcounter{coroCount}
    \begin{trivlist}
    \item[\hskip \labelsep
        {\bfseries Corollary \arabic{coroCount} #1}]}
    {\end{trivlist}}

\newenvironment{example}[1][Example]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Remark]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

\newcommand{\eat}[1]{}

\begin{document}

\title{Efficient Evaluation of Skyline Queries in Wireless Data Broadcast Environments}

\numberofauthors{2}

\author
{
 \alignauthor Chih-Jye Wang\\
 \affaddr{Dept. of Computer Science and Software Engineering}\\
 \affaddr{Auburn University}\\
 \affaddr{Auburn, AL 36849, USA}\\
 \email{wangchj@auburn.edu}
 \alignauthor Wei-Shinn Ku\\
 \affaddr{Dept. of Computer Science and Software Engineering}\\
 \affaddr{Auburn University}\\
 \affaddr{Auburn, AL 36849, USA}\\
 \email{weishinn@auburn.edu}
}

\conferenceinfo{GIS'12,} {November 6-9, 2012. Redondo Beach, CA,
USA}\CopyrightYear{2012}

\maketitle

\begin{abstract}
Skyline is a popular query type which retrieves data objects that
are not dominated by any other object with respect to multiple
attributes. Skyline queries have broad applications; however,
limited studies have been done on skyline in the broadcast data
model. No study has been done on flexible skyline query
evaluations in this model that can handle a combination of minimum
and maximum attributes. In this paper, we propose the depth-first
distributed index (DFDI) and the skyline algorithms that
incorporate DFDI to efficiently evaluate skyline in broadcast
environments. Our extensive simulations show that the proposed
algorithms can answer skyline queries in broadcast environments
effectively and efficiently.
\end{abstract}

\category{H.2.8}{Database Management}{Database
Application}[Spatial databases and GIS]

\terms{Algorithms and Experimentation}

\keywords{Data broadcast, Skyline query, Location-based services.} % NOT required for Proceedings

\section{Introduction}\label{sec-intro}
\input{intro}

\section{Preliminary}\label{sec-prelim}
\input{prelim}

\section{Tree-based Distributed Index}\label{sec-index}
\input{depth}

\section{Pruning Region Broadcast Skyline}\label{sec-pruning}
\input{pruning}

\section{Experimental Evaluation}\label{sec-exp}
\input{experiment}

\section{Related Work}\label{sec-related}
\input{related}

\section{Conclusion}\label{sec-conc}
\input{conc}

\section*{Acknowledgements}
\input{ack}

%\small {\section*{Acknowledgments}


\bibliographystyle{abbrv}
\bibliography{bibliography}

\end{document}
