In this paper, we presented a broadcast data stream allocation
technique (DFDI) that utilizes the R-tree and performs a
depth-first traversal of the index to create a distributed index.
The goals of DFDI are to facilitate query processing from
broadcast data, to reduce the index overhead (IP) and to improve
the initial index probe. DFDI is able to achieve all these with
reasonable efficiency. DFDI is a flexible R-tree based index and
supports skyline queries as well as other data query types. The
allocation distributes $b^h$ number of index segments among the
broadcast program to reduce the initial index, and at the same
time keeps the index overhead low. The simulation results for
index percentage show that DFDI performs very well with two levels
of replication and follow the efficiency of one-time index with
only a $16\%$ increase in index overhead.

The simulation results show that the approach also performs well
with data of higher dimensions. The index overhead decreases as
the number of records remain constant and the number of data
dimensions increase. This is due to the fact that the growth of
dimensionality does not make the index tree grow ``taller" and
does not incur the cost of new nodes when the index grows. The
height of an index tree does increase as the number of records
increase, but as seen in Figure~\ref{fig:ip_rc}, the growth of the
index is not as fast as the growth of the amount of data;
therefore, the index overhead decreases as records increase.

In addition, we introduced point-based and index-based pruning
skyline algorithms. The experiments show that both algorithms are
capable of evaluating skyline queries of combined $min$ and $max$
attributes with reasonable tuning time and dominance tests. The
index-based skyline has always performed better than the
point-based skyline, in some cases by several factors. The
performance of the algorithms is also affected by the data
arrangement and R-tree implementation. From our simulation, we
find that R-trees that index records with lower attributes first
perform better for $min$ skyline queries, and vice versa.
